Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-19 WSSSPE3/report/wg_main_training.tex
edit to edit

\item  International Workshop on Software Engineering for High
Performance Computing in Computational Science and
Engineering(SEHPCCSE)\footnote{\url{http://wssspe.researchcomputing.org.uk/}}
\katznote{fix URL and change to cite}

>>>>

\item  International Workshop on Software Engineering for High
Performance Computing in Computational Science and
Engineering (SEHPCCSE)\footnote{\url{http://wssspe.researchcomputing.org.uk/}}
\katznote{fix URL and change to cite}
